\thispagestyle{logoheader}
%\vspace*{-2em} % Pulls the "Welcome!" title closer to the header
\section*{Welcome!}

\noindent The following pages are filled with delicious soup recipes that were submitted to the first annual SoupCon in Ann Arbor, MI on December 15, 2024. SoupCon started out as a joke born from a complaint I had that 1) there weren't enough ‘weird’ open community events around town anymore (looking at you homemade pickle/jam competition held at Downtown Home and Garden nearly 10 years ago) and 2) having left academia I was craving the feeling of a conference. So, I set out to bother every person who would listen about meeting up to trade soups in the middle of December. What came of it was a great evening of 30 or so people sharing soups and stories with one another. A real who's who of soup if you will. Each soupmaker submitted an abstract ahead of the meeting (what soup they were bringing and why), as well as a recipe for how to make what they brought. As entries came in, the program committee grouped soups together into “like” categories so that they could be organized for the night of the event. As such, a soup that is vegetarian in composition might be grouped in American Regional Delicacies or Mediterranean soups rather than strictly Vegetarian. Like every good conference, this document serves as a published proceedings, to report to the public what soups are being made around town as well as giving you, the reader, the chance to make them for yourself at home.

\vspace{1em}
\noindent If you’re reading this, I imagine you’ve found your way here by a sticker placed somewhere around town, a conversation with someone who was at SoupCon, or you fortuitously arrived here via some long tumble through the internet. However you got here, welcome! Enjoy the soups and stories on the pages that follow and hopefully, if there is a SoupCon 2 in 2025, (which we very much hope there will be), we hope to see you there sharing a soup with us this coming winter.

\vspace{1em}
\noindent For updates on SoupCon for 2025 check out \href{http://soupcona2.org}{soupcona2.org} or email \href{mailto:soupcona2@gmail.com}{soupcona2@gmail.com}.

\vspace{1em}

\noindent Cheers,

\vspace{1em}

\begin{itemize}[label={--}, leftmargin=2em]
    \item Justin Craft \\
    SoupCon Program Chair
\end{itemize}

\newpage
